Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-08-31 public/paper/pyg4ometry.tex
Paper update

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Geant; Fluka; GDML; CAD; STEP; Monte Carlo; Particle; Transport; Geometry;

@@

\begin{itemize}
\item disjoint subtractions?
\item quadric specialisation
\item second order lattice
\item Materials 
\end{itemize}

@@

\subsection{Disjunctive normal form and degenerate surfaces}
Typically FLUKA will decompose a \verb|REGION| into disjunctive normal form (DNF), this normal form is characterised as the union of intersections, so 
\begin{equation}
R = z_1 \; | \;z_2\;  | \; z_3 | \; z_4 \dots
\end{equation}
Defining \verb|REGION|s in terms of DNF allows the rapid test if a point is inside or outside. Testing each zone $z_i$ of $R$ can terminate if a point 
is determined to be inside any of convex zones. In general Equation~\ref{eqn:logicalSubtraction} is not in a DNF. If there are many levels of logical-physical 
volume placement, then recursive application of  Equation~\ref{eqn:logicalSubtraction} will create a nested set of parentheses. There are some conditions 
where a general boolean expression can yield an exponential explosion of the final DNF. There are well known algorithms to convert logical expressions to 
DNF  \colorbox{yellow}{XXX}. Pyg4ometery can simplify parentheses from a \verb|REGION| by creating a sympy \colorbox{yellow}{XXX CITE} expression and 
using its logical module. Before version 4.0 FLUKA would simplify all regions to DNF and some converted geometry would generate too many zones and would fail.
FLUKA version 4 allows control of the NDF expansion.

@@

\subsection{Disucssion}
There are still a few outstanding issues with Geant4/GDML to Fluka conversion.

\begin{itemize}
\item Degenerate body look up 
\item Bodes with/without transformation 
\item Non-convex solids, convex decomposition (TwistedBox, TwistedTrap, TwistedTrd, TwistedTube, Tessellated)
\item Scaled solid, Placement scale 
\item Replica, Division, Parameterised
\item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \label{eqn:logicalSubtraction} speed up using meshes
\end{itemize}

@@

@@

\begin{enumerate}
\item Graphical front end viewer
\item C++ output
\item CAD BREP to FLUKA converter (a la McCAD) 
\item Integration of other tools (DAGMC) 
\item Far from perfect conversions. 
\end{enumerate}

>>>>

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Geant; FLUKA; GDML; CAD; STEP; Monte Carlo; Particle; Transport; Geometry;

@@

\begin{enumerate}
\item disjoint subtractions?
\item quadric specialisation
\item second order lattice
\item Materials 
\end{enumerate}

@@

\subsection{Disjunctive normal form and degenerate surfaces}
Typically FLUKA will decompose a \verb|REGION| into disjunctive normal form (DNF), this normal form is characterised as the union of intersections, so 
\begin{equation}
R = z_1 \; | \;z_2\;  | \; z_3 | \; z_4 \dots
\end{equation}
Defining \verb|REGION|s in terms of DNF allows the rapid test if a point is inside or outside. Testing each zone $z_i$ of $R$ can terminate if a point 
is determined to be inside any of convex zones. In general Equation~\ref{eqn:logicalSubtraction} is not in a DNF. If there are many levels of logical-physical 
volume placement, then recursive application of  Equation~\ref{eqn:logicalSubtraction} will create a nested set of parentheses. There are some conditions 
where a general boolean expression can yield an exponential explosion of the final DNF. There are well known algorithms to convert logical expressions to 
DNF  \colorbox{yellow}{XXX}. Pyg4ometery can simplify parentheses from a \verb|REGION| by creating a sympy \colorbox{yellow}{XXX CITE} expression and 
using its logical module. Before version 4.0 FLUKA would simplify all regions to DNF and some converted geometry would generate too many zones and would fail.
FLUKA version 4 allows control of the DNF expansion.

@@

\subsection{Disucssion}
There are still a few outstanding issues with Geant4/GDML to FLUKA conversion.

\begin{enumerate}
\item Degenerate body look up 
\item Bodes with/without transformation 
\item Non-convex solids, convex decomposition (TwistedBox, TwistedTrap, TwistedTrd, TwistedTube, Tessellated)
\item Scaled solid, Placement scale 
\item Replica, Division, Parameterised
\item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \label{eqn:logicalSubtraction} speed up using meshes
\end{enumerate}

@@

\begin{enumerate}
\item Merging Registries 
\item Removing volumes 
\item Editing solid
\item Converting to assembly solids 
\end{enumerate}

@@

\begin{enumerate}
\item Graphical front end viewer
\item C++ output
\item CAD BREP to FLUKA converter (a la McCAD) 
\item Integration of other tools (DAGMC) 
\item Far from perfect conversions
\end{enumerate}
